WEEK2
map difference in life expentancy in London

1.Execute basic processing in R
2.Examine, clean and manipulate comma seperate value (.csv) data
3.Examine, clean and manipulate and plot spatial (.shp) data
4.Produce interactive maps
5.Evaluate the benefits of different data manipulation and mapping techniques

DATA
LondonData <- read_csv("https://data.london.gov.uk/download/ward-profiles-and-atlas/772d2d64-e8c6-46cb-86f9-e52b4c7851bc/ward-profiles-excel-version.csv")

## packages

```{r}
library(here)
library(dplyr)
library(tidyverse)
library(sf)
library(sp)
library(janitor)
library(maptools)
library(RColorBrewer)
library(classInt)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(rgdal)
library(geojsonio)
library(plotly)

# rm(list = ls())
```

## read data

```{r}
#row_to_delete <- LondonData[]
LondonData <- read.csv("wk2/data/LondonData.csv",
                          header = TRUE,
                          sep=",",
                          encoding = "latin1")
# header = TRUE   the first row of the CSV file contains column names (headers). When set to TRUE, it tells R to treat the first row as column names
#encoding = "latin1"   specifies the character encoding of the file

#here::here()
##LondonDataOSK<- read.csv(here::here("wk2","data","LondonData.csv"))
```

## examing new data

```{r}
# check what data type your new data set
class(LondonData)
# another two functions summarise_all() (from dplyr) and pivot_longer() (from tidyr) to check that our data has been read in correctly
Datatypelist <- LondonData %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")
Datatypelist
```

## edit data

```{r}
LondonData <- edit(LondonData)
```

## summarize data

```{r}
summary(LondonData)
LondonData%>%
  colnames()%>%
  # just look at the head, top5
  head()
```

## manipulate data

```{r}
# 1. select rows
    #[]
  ##LondonBoroughs <- LondonData[626:658,]
    #dplyr--slice()
  LondonBoroughs <- LondonData %>% 
    slice(626:658)

# 2. filter
  Femalelifeexp<- LondonData %>%  
   dplyr:::filter.data.frame(.,`Female.life.expectancy..2009.13`>90) 
    #use backticks`` when column names contain spaces or special characters
    ## cannot use in character format

 ##  str_detect
  LondonBoroughs <- LondonData %>% 
    filter(str_detect(`New.code`, "^E09"))
    # ^E09 "New code" starts with "E09"
```

```{r}
# 3. select field
  LondonBoroughs$Ward.name
  ##  $
  # same as
  LondonBoroughs %>% 
    dplyr::select(`Ward.name`) %>% 
    print()
  
  # two rows at the top for the City of London, it features twice in the data set
  # extract only unique rows
  LondonBoroughs <- LondonBoroughs %>% 
    distinct()
  
# 4. select columns
  LondonBoroughs_manualcols <- LondonBoroughs[,c(1,19,20,21)]
  
  LondonBoroughs_dplyrcols <- LondonBoroughs %>% 
    dplyr::select(c(1,19,20,21))
  
  ## select columns with certain words
  LondonBoroughs_contains <- LondonBoroughs %>% 
    dplyr::select(contains("expectancy",
                           contains("Ward.name")))
```

```{r}
# 5 rename columns
LondonBoroughs <- LondonBoroughs %>%
  dplyr::rename(borough=`Ward.name`) %>% 
  clean_names
  ## By defualt Janitor removes all capitals and uses an underscore wherever there is a space

#janitor::clean_names
  #LondonBoroughs <- LondonBoroughs %>% janitor::clean_names(., case="big_camel")
  ## case="big_camel" = "column_name_example" might become "ColumnNameExample"
```

```{r}
# 6. dplyr::mutate()
  # add new variables based on existing ones

## a.the average of male and female life expectancy together
## b.a normalised value for each London borough based on the London average.


is.numeric(Femalelifeexp) # false

Life_expectancy <- LondonBoroughs %>% 
  #new column with average of male and female life expectancy
  mutate(averagelifeexpectancy=(female_life_expectancy_2009_13+male_life_expectancy_2009_13)/2) %>% 
  #new column with normalised life expectancy
  mutate(normaliselifeexpectancy=averagelifeexpectancy/mean(averagelifeexpectancy)) %>% 
  #select only columns we want
  dplyr::select(new_code,
                borough,
                averagelifeexpectancy,
                normaliselifeexpectancy) %>% 
  #arrange in descending order
  #ascending is the default and would be
  #arrange(normalisedlifeepectancy)
  arrange(desc(normaliselifeexpectancy))

# show the top and bottom number of rows
slice_head(Life_expectancy,n=5)
slice_tail(Life_expectancy,n=5)
```

```{r}
# 7. dplyr::case_when()
Life_expectancy2 <- Life_expectancy %>%
  mutate(UKcompare=case_when(averagelifeexpectancy>81.16~"above UK average",TRUE~"below UK average"))

```

```{r}
# 8. group_by
Life_expectancy2_group <- Life_expectancy2 %>%
  mutate(UKdiff = averagelifeexpectancy-81.16) %>%
  group_by(UKcompare)%>%
  summarise(range=max(UKdiff)-min(UKdiff), count=n(), Average=mean(UKdiff))

```

have more information based on the distribution of the Boroughs compared to the national average, as opposed to just over or under

1.Round the column UKdiff to 0 decimal places (not adding a new column)
2.Use case_when() to find Boroughs that have an average age of equal to or over 81 and create a new column that contains text based combining equal or above UK average by then the years created in UKdiff. We do this through the str_c() function from the stringr package that let’s us join two or more vector elements into a single character vector. Here sep determines how these two vectors are separated.
3.Then group by the UKcompare column
4.Finally, count the number in each group.

```{r}
Life_expectancy3 <- Life_expectancy %>%
  mutate(UKdiff = averagelifeexpectancy-81.16)%>%
  mutate(across(where(is.numeric), round, 3))%>%
  mutate(across(UKdiff, round, 0))%>%
  mutate(UKcompare = case_when(averagelifeexpectancy >= 81 ~ 
                                 str_c("equal or above UK average by",
                                       UKdiff, 
                                       "years", 
                                       sep=" "), 
                               TRUE ~ str_c("below UK average by",
                                            UKdiff,
                                            "years",
                                            sep=" ")))%>%
  group_by(UKcompare)%>%
  summarise(count=n())
```

```{r}
Life_expectancy4 <- Life_expectancy %>%
  mutate(UKdiff = averagelifeexpectancy-81.16)%>%
  mutate(across(is.numeric, round, 3))%>%
  mutate(across(UKdiff, round, 0))
```

## plot

```{r}
plot(LondonBoroughs$male_life_expectancy_2009_13,
     LondonBoroughs$percent_children_in_reception_year_who_are_obese_2011_12_to_2013_14)
```

```{r}
plot_ly(LondonBoroughs, 
        #data for x axis
        x = ~male_life_expectancy_2009_13, 
        #data for y axis
        y = ~x_children_in_reception_year_who_are_obese_2011_12_to_2013_14, 
        #attribute to display when hovering 
        text = ~borough, 
        type = "scatter", 
        mode = "markers")
```


```{r}
EW <- st_read("wk7/data/statistical-gis-boundaries-london/ESRI/London_Borough_Excluding_MHW.shp")
```

```{r}
LondonMap<- EW %>%
  filter(str_detect(GSS_CODE, "^E09"))

#plot it using the qtm function
qtm(LondonMap)
```

```{r}
LondonData <- clean_names(LondonData)

#EW is the data we read in straight from the web
BoroughDataMap <- EW %>%
  clean_names()%>%
  # the . here just means use the data already loaded
  filter(str_detect(gss_code, "^E09"))%>%
  merge(.,
        LondonData, 
        by.x="gss_code", 
        by.y="new_code",
        no.dups = TRUE)%>%
  distinct(.,gss_code,
           .keep_all = TRUE)
```

```{r}
BoroughDataMap2 <- EW %>% 
  clean_names() %>%
  filter(str_detect(gss_code, "^E09"))%>%
  left_join(., 
            LondonData,
            by = c("gss_code" = "new_code"))
```

```{r}
tmap_mode("plot")
qtm(BoroughDataMap, 
    fill = "rate_of_job_seekers_allowance_jsa_claimants_2015")
```

extract it from OpenStreetMap (OSM) using the read_osm() function from the tmaptools package

create a box (termed bounding box) around London using the st_box() function from the sf package to extract the basemap image (which is a raster)

```{r}
tmaplondon <- BoroughDataMap %>%
  st_bbox(.) %>% 
  tmaptools::read_osm(., type = "osm", zoom = NULL)
```

```{r}
tmap_mode("plot")

tm_shape(tmaplondon)+
tm_rgb()+
tm_shape(BoroughDataMap) + 
tm_polygons("rate_of_job_seekers_allowance_jsa_claimants_2015", 
        style="jenks",
        palette="YlOrBr",
        midpoint=NA,
        title="Rate per 1,000 people",
        alpha = 0.5) + 
  tm_compass(position = c("left", "bottom"),type = "arrow") + 
  tm_scale_bar(position = c("left", "bottom")) +
  tm_layout(title = "Job seekers' Allowance Claimants", legend.position = c("right", "bottom"))
```


```{r}
Life_expectancy4map <- EW %>%
    inner_join(., 
            Life_expectancy4,
            by = c("GSS_CODE" = "new_code"))%>%
    distinct(.,GSS_CODE, 
           .keep_all = TRUE)
```

```{r}
tmap_mode("plot")

tm_shape(tmaplondon)+
tm_rgb()+
tm_shape(Life_expectancy4map) + 
tm_polygons("UKdiff", 
        style="pretty",
        palette="Blues",
        midpoint=NA,
        title="Number of years",
        alpha = 0.5) + 
  tm_compass(position = c("left", "bottom"),type = "arrow") + 
  tm_scale_bar(position = c("left", "bottom")) +
  tm_layout(title = "Difference in life expectancy", legend.position = c("right", "bottom"))
```


Force the columns to the appropriate data types (e.g. text, numeric)
```{r}
flytipping <- read_csv("https://data.london.gov.uk/download/fly-tipping-incidents/536278ff-a391-4f20-bc79-9e705c9b3ec0/fly-tipping-borough.csv")

flytipping1 <- read_csv("https://data.london.gov.uk/download/fly-tipping-incidents/536278ff-a391-4f20-bc79-9e705c9b3ec0/fly-tipping-borough.csv", 
                       col_types = cols(
                         code = col_character(),
                         area = col_character(),
                         year = col_character(),
                         total_incidents = col_number(),
                         total_action_taken = col_number(),
                         warning_letters = col_number(),
                         fixed_penalty_notices = col_number(),
                         statutory_notices = col_number(),
                         formal_cautions = col_number(),
                         injunctions = col_number(),
                         prosecutions = col_number()
                       ))
```



