# Chapter 3 Spatial descriptive statistics

1.  Load, manipulate and interpret raster layers
2.  Observe and critique different descriptive data manipulation methods and outputs

DATA 1. vector of Australia,download the GeoPackage <https://gadm.org/download_country_v3.html>

# 1. Projection

## packages

```{r}
library(sf)
library(here)
library(terra)
library(raster)
library(tidyverse)
library(fs)
```

## read file

```{r}
st_layers("wk3/data/gadm36_AUS.gpkg") # what's inside

Ausoutline <- st_read(("wk3/data/gadm36_AUS.gpkg"), 
                      layer='gadm36_AUS_0')
```

## check CRS

```{r}
print(Ausoutline)
# check that the coordinate reference systems of sf or sp objects using the print function

# proj4 string -- a compact way of identifying a crs
st_crs(Ausoutline)$proj4string
# "+proj=longlat +datum=WGS84 +no_defs"
```

## assign a crs EPSG

```{r}
Ausoutline <- st_read(("wk3/data/gadm36_AUS.gpkg"), 
                      layer='gadm36_AUS_0') %>% st_set_crs(4326)
```

However for generating maps in packages like `leaflet`, your maps will need to be in WGS84, rather than a projected (flat) reference system .

## 1.1 reproject

```{r}
AusoutlinePROJECTED <- Ausoutline %>% 
  st_transform(.,3112) # WGS84->GDA94 EPSG 3112
# st_transform reproject simple features, not spatraster

print(AusoutlinePROJECTED)
```

## sf to sp

```{r}
# In the SF object, compare the values in the geometry column with those in the original file to look at how they have changed

#From sf(simple features: dataframe) to sp(spatial: list inside list)
AusoutlineSP <- Ausoutline %>%
  as(., "Spatial")

#From sp to sf
AusoutlineSF <- AusoutlineSP %>%
  st_as_sf()

# use sf in tidyverse
```

# 1.2 worldclim data

## read data

WorldClim data --- this is a dataset of free global climate layers (rasters) with a spatial resolution of between 1km2 and 240km2 <https://www.worldclim.org/data/worldclim21.html>

```{r}
jan <- terra::rast("wk3/data/wc2.1_5m_tavg_01.tif")
jan
```

```{r}
plot(jan)
```

`Mollweide projection` retains area proportions whilst compromising accuracy of angle and shape

```{r}
# set the proj 4 to a new object

pr1 <- terra::project(jan, "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")

#or....

newproj<-"ESRI:54009"
# get the jan raster and give it the new proj4
pr1 <- jan %>%
  terra::project(., newproj)
plot(pr1)

# to WGS84
pr1 <- pr1 %>%
  terra::project(., "EPSG:4326")
plot(pr1)
```

# 1.3 data loading

```{r}
# look in our folder, find the files that end with .tif and 
dir_info("wk3/data/") 
```

## listfile

```{r}
# dplyr::select

listfiles<-dir_info("wk3/data/") %>% 
  filter(str_detect(path,".tif")) %>% 
  dplyr::select(path)%>% 
  dplyr::pull()

# pull() from dplyr which is the same as the $ often used to extract columns as in the next stage the input must be filenames as characters (nothing else like a column name)
listfiles
```

## load data into SpatRaster

"空间栅格" 或 "空间光栅"

```{r}
# A SpatRaster is a collection of raster layers with the same spatial extent and resolution
worldclimtemp <- listfiles %>% 
  terra::rast()

worldclimtemp
```

## access single layer

```{r}
worldclimtemp[[1]]
```

## rename layers within the stack

```{r}
month <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", 
           "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")

names(worldclimtemp) <- month

# dplyr::rename() not for raster data

worldclimtemp$Jan
```

# 1.4 raster location

```{r}
site <- c("Brisbane", "Melbourne", "Perth", "Sydney", "Broome", "Darwin", "Orange", 
          "Bunbury", "Cairns", "Adelaide", "Gold Coast", "Canberra", "Newcastle", 
          "Wollongong", "Logan City" )
lon <- c(153.03, 144.96, 115.86, 151.21, 122.23, 130.84, 149.10, 115.64, 145.77, 
         138.6, 153.43, 149.13, 151.78, 150.89, 153.12)
lat <- c(-27.47, -37.91, -31.95, -33.87, 17.96, -12.46, -33.28, -33.33, -16.92, 
         -34.93, -28, -35.28, -32.93, -34.42, -27.64)
#Put all of this inforamtion into one list 
samples <- data.frame(site, lon, lat, row.names="site")
# Extract the data from the Rasterstack for all points 
AUcitytemp<- terra::extract(worldclimtemp, samples) # zonal statistics
```

terra::extract() is a function that extracts values from a SpatRaster for a set of points, lines or polygons. It is a wrapper for the extract function in the raster package. The function is vectorised, so you can extract values for multiple points, lines or polygons at once.

## add the city names

```{r}
Aucitytemp2 <- AUcitytemp %>% 
  as_tibble()%>% 
  add_column(Site = site, .before = "Jan")
```

# 2. descriptive statistics

## 2.1 data preparation

```{r}
# perth
Perthtemp <- Aucitytemp2 %>%
  filter(site=="Perth")
# or
# Perthtemp <- Aucitytemp2[3,]
```

## 2.2 histogram

```{r}
# tibble stored the data as double and the base hist() function needs it as numeric
hist(as.numeric(Perthtemp))
```

The x axis is the temperature and the y is the frequency of occurrence.

There seems to be an outlier with this plot as we haven't removed the columns we don't need - look in the Perthtemp tibble and you will see an `ID of 3` which is plotted above.

```{r}
### improve aesthetic

# outliner ID 3

#define where the breaks in histogram
userbreak <- c(8,10,12,14,16,18,20,22,24,26)

#remove the ID and the site columns
Perthtemp <- Aucitytemp2 %>% 
  filter(site=="Perth")

t <- Perthtemp %>% 
  dplyr::select(Jan:Dec)

hist((as.numeric(t)),
     breaks=userbreak,
     col="red",
     main="Histogram of Perth Temperature",
     xlab="Temperature",
     ylab="Frequency")
```

### check out the histogram

```{r}
histinfo <- as.numeric(t) %>% 
  as.numeric()%>% 
  hist(.,
       breaks=userbreak,
       col="red",
       main="Histogram of Perth Temperature",
       xlab="Temperature",
       ylab="Frequency")

histinfo
```

## 2.3 using more data

```{r}
plot(Ausoutline$geom)
```

### st_simplify

```{r}
AusoutSIMPLE <- Ausoutline %>% 
  st_simplify(.,preserveTopology=TRUE,dTolerance = 1000) %>% 
  # the argument dTolerance controls the level of generalisation in the units of the map, the higher the number the more generalised the map
  # preserveTopology to TRUE or FALSE, when true it means that polyongs aren’t removed and holes in polygons are retained
  st_geometry() %>% 
  plot()
```

### projection conflict

```{r}
# make sure both layers in same CRS
print(Ausoutline)

crs(worldclimtemp)
```

### crop data

clip the data to) to the outline of Australia then crop our WorldClim dataset to it

crop:适用于需要从整个数据集中选择或提取特定地理区域的情况。例如，从全球的栅格数据中裁剪出特定国家或区域的数据

```{r}
Austemp <- Ausoutline %>% 
  #crop temp data to the extent
  terra::crop(worldclimtemp,.) # terra::crop(worldclimtemp,Ausoutline)

#plot the output
plot(Austemp)
```

### extract by mask

the raster hasn't been perfectly clipped to the exact outline of Australia, so we will use the `mask` function to clip the raster to the exact outline of Australia.

mask:适用于需要将数据中的某些区域标记为无效或排除在分析之外的情况。例如，通过一个多边形区域来定义一个掩膜，将该区域以外的数据设为缺失值。

```{r}
exactAus <- terra::mask(Austemp,Ausoutline)
# mask(tif,shp)
```

### plot march

```{r}
# subset using the known location of the raster
hist(exactAus[[3]],col="red",main="March Temperature")
```

## 2.4 histogram with ggplot

### convert to tibble

```{r}
# make our raster into a data.frame to be compatible with ggplot2, using a dataframe or tibble
exactAusdf <- exactAus %>% 
  as.data.frame()
```

### ggplot

```{r}
library(ggplot2)
```

### 2.4.1 plot1 single month with mean

```{r}
gghist <- ggplot(exactAusdf,
                 aes(x=Mar))+
  geom_histogram(color="black",
                 fill="white")+
  labs(title="Ggplot2 histogram of Australian March temperatures",
       x="Temperature",
       y="Frequency")

# add a vertical line to the hisogram showing mean temperature
gghist + 
  geom_vline(aes(xintercept=mean(Mar,
                                      na.rm=TRUE)),
             # any missing values should be ignored when calculating the mean
                  color="blue",
                  linetype="dashed",
                  size=1)+  # line thickness
  theme(plot.title = element_text(hjust=0.5))
  # centers the title by setting the horizontal justification (hjust) to 0.5
```

### 2.4.2 plot2 multiple months

#### pivot_longer

```{r}
# plot multiple months of temperature data on the same histogram

## put our variable (months) into a one column using pivot_longer()
## select columns 1-12 (all the months) and place them in a new column called Month and their values in another called Temp

squishdata <- exactAusdf %>% 
  pivot_longer(
    cols = 1:12,
    names_to = "Month",
    values_to = "Temp"
  )
```

#### suset and select 2 months

```{r}
twomonths <- squishdata %>% 
  filter(.,Month=="Jan" | Month=="Jun")
```

#### mean of each month

```{r}
meantwomonths <- twomonths %>% 
  group_by(Month) %>% 
  summarise(Mean=mean(Temp,
                      na.rm=TRUE))
# any missing values should be ignored when calculating the mean
```

#### plot

```{r}
ggplot(twomonths,
       aes(x=Temp,color=Month,fill=Month))+
  # color=Month and fill=Month: The "Month" variable is used to differentiate the two months by color and fill.
  geom_histogram(position="identity", 
                 # ensures that the bars are positioned directly over the x-values without any stacking.
                 alpha=0.5)+
  geom_vline(data=meantwomonths,
             aes(xintercept= Mean,
                 color=Month),
             linetype="dashed")+
  labs(title="Ggplot2 histogram of Australian Jan and Jun temperatures",
       x="Temperature",
       y="Frequency")+
  theme_classic()+
  # classic theme provides a simple and clean appearance to the plot
  theme(plot.title = 
          # "plot.title" refers to the title that you set using the labs(title = ...) function 
          element_text(hjust = 0.5))# element_text function to specify text properties
  # theme function customize various aspects of the plot's appearance, such as text size, colors, axis labels, and more
  
```

1. dropped all the NAs with drop_na()

2. made sure that the Month column has the levels specified, which will map in descending order (e.g. Jan, Feb, March..)

3. selected a bin width of 5 and produced a faceted plot 分面直方图
直方图被分成多个小图（facet），每个小图表示数据中的一个子集。这些子集由一个或多个分类变量定义。例如，如果我们想要查看每个月的温度分布，我们可以使用月份作为分类变量来分面直方图。
```{r}
data_complete_cases <- squishdata %>%
  drop_na()%>% 
  mutate(Month = factor(Month, levels = c("Jan","Feb","Mar",
                                          "Apr","May","Jun",
                                          "Jul","Aug","Sep",
                                          "Oct","Nov","Dec")))

# Plot faceted histogram
ggplot(data_complete_cases, aes(x=Temp, na.rm=TRUE))+
  geom_histogram(color="black", binwidth = 5)+
  labs(title="Ggplot2 faceted histogram of Australian temperatures", 
       x="Temperature",
       y="Frequency")+
  facet_grid(Month ~ .)+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
library(plotly)
# split the data for plotly based on month

jan <- squishdata %>%
  drop_na() %>%
  filter(., Month=="Jan")

jun <- squishdata %>%
  drop_na() %>%
  filter(., Month=="Jun")

# give axis titles
x <- list (title = "Temperature")
y <- list (title = "Frequency")

# set the bin width
xbinsno<-list(start=0, end=40, size = 2.5)

# plot the histogram calling all the variables we just set
ihist<-plot_ly(alpha = 0.6) %>%
        add_histogram(x = jan$Temp,
        xbins=xbinsno, name="January") %>%
        add_histogram(x = jun$Temp,
        xbins=xbinsno, name="June") %>% 
        layout(barmode = "overlay", xaxis=x, yaxis=y)

ihist
```


```{r}
# mean per month
meanofall <- squishdata %>%
  group_by(Month) %>%
  summarise(mean = mean(Temp, na.rm=TRUE))

# print the top 1
head(meanofall, n=1)
```
```{r}
# standard deviation per month
sdofall <- squishdata %>%
  group_by(Month) %>%
  summarize(sd = sd(Temp, na.rm=TRUE))

# maximum per month
maxofall <- squishdata %>%
  group_by(Month) %>%
  summarize(max = max(Temp, na.rm=TRUE))

# minimum per month
minofall <- squishdata %>%
  group_by(Month) %>%
  summarize(min = min(Temp, na.rm=TRUE))

# Interquartlie range per month
IQRofall <- squishdata %>%
  group_by(Month) %>%
  summarize(IQR = IQR(Temp, na.rm=TRUE))

# perhaps you want to store multiple outputs in one list..
lotsofstats <- squishdata %>%
  group_by(Month) %>%
  summarize(IQR = IQR(Temp, na.rm=TRUE), 
            max=max(Temp, na.rm=T))

# or you want to know the mean (or some other stat) 
#for the whole year as opposed to each month...

meanwholeyear=squishdata %>%
  summarize(meanyear = mean(Temp, na.rm=TRUE))
```

