# 1. Projection
## packages
```{r}
library(sf)
library(here)
```
## read file
```{r}
st_layers("wk3/data/gadm36_AUS.gpkg") # what's inside

Ausoutline <- st_read(("wk3/data/gadm36_AUS.gpkg"), 
                      layer='gadm36_AUS_0')
```
## check CRS
```{r}
print(Ausoutline)
# check that the coordinate reference systems of sf or sp objects using the print function

# proj4 string -- a compact way of identifying a crs
st_crs(Ausoutline)$proj4string
# "+proj=longlat +datum=WGS84 +no_defs"
```
## assign a crs  EPSG
```{r}
Ausoutline <- st_read(("wk3/data/gadm36_AUS.gpkg"), 
                      layer='gadm36_AUS_0') %>% st_set_crs(4326)
```
## 1.1 reproject
```{r}
AusoutlinePROJECTED <- Ausoutline %>% 
  st_transform(.,3112) # WGS84->GDA94 EPSG 3112
# st_transform reproject simple features, not spatraster

print(AusoutlinePROJECTED)
```
## sf to sp
```{r}
# In the SF object, compare the values in the geometry column with those in the original file to look at how they have changed

#From sf(simple features: dataframe) to sp(spatial: list inside list)
AusoutlineSP <- Ausoutline %>%
  as(., "Spatial")

#From sp to sf
AusoutlineSF <- AusoutlineSP %>%
  st_as_sf()

# use sf in tidyverse
```
# 1.2 worldclim data
## packages
```{r}
library(terra)
library(raster)
```
## read data
```{r}
jan <- terra::rast("wk3/data/wc2.1_5m_tavg_01.tif")
jan
```

```{r}
plot(jan)
```

```{r}
# set the proj 4 to a new object

pr1 <- terra::project(jan, "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")

#or....

newproj<-"ESRI:54009"
# get the jan raster and give it the new proj4
pr1 <- jan %>%
  terra::project(., newproj)
plot(pr1)

# to WGS84
pr1 <- pr1 %>%
  terra::project(., "EPSG:4326")
plot(pr1)
```
# 1.3 data loading
```{r}
library(tidyverse)
library(fs)

# look in our folder, find the files that end with .tif and 
dir_info("wk3/data/") 
```
## listfile
```{r}
# dplyr::select

listfiles<-dir_info("wk3/data/") %>% 
  filter(str_detect(path,".tif")) %>% 
  dplyr::select(path)%>% 
  dplyr::pull()

# pull() from dplyr which is the same as the $ often used to extract columns as in the next stage the input must be filenames as characters (nothing else like a column name)
listfiles
```
## load data into SpatRaster
```{r}
# A SpatRaster is a collection of raster layers with the same spatial extent and resolution
worldclimtemp <- listfiles %>% 
  terra::rast()

worldclimtemp
```
## access single layer
```{r}
worldclimtemp[[1]]
```
## rename layers within the stack
```{r}
month <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", 
           "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")

names(worldclimtemp) <- month

# dplyr::rename() not for raster data

worldclimtemp$Jan
```
# 1.4 raster location
```{r}
site <- c("Brisbane", "Melbourne", "Perth", "Sydney", "Broome", "Darwin", "Orange", 
          "Bunbury", "Cairns", "Adelaide", "Gold Coast", "Canberra", "Newcastle", 
          "Wollongong", "Logan City" )
lon <- c(153.03, 144.96, 115.86, 151.21, 122.23, 130.84, 149.10, 115.64, 145.77, 
         138.6, 153.43, 149.13, 151.78, 150.89, 153.12)
lat <- c(-27.47, -37.91, -31.95, -33.87, 17.96, -12.46, -33.28, -33.33, -16.92, 
         -34.93, -28, -35.28, -32.93, -34.42, -27.64)
#Put all of this inforamtion into one list 
samples <- data.frame(site, lon, lat, row.names="site")
# Extract the data from the Rasterstack for all points 
AUcitytemp<- terra::extract(worldclimtemp, samples) # zonal statistics
```
## add the city names
```{r}
Aucitytemp2 <- AUcitytemp %>% 
  as_tibble()%>% 
  add_column(Site = site, .before = "Jan")
```
# 2. descriptive statistics
## 2.1 data preparation
```{r}
# perth
Perthtemp <- Aucitytemp2 %>%
  filter(site=="Perth")
# or
# Perthtemp <- Aucitytemp2[3,]
```
## 2.2 histogram
```{r}
# tibble stored the data as double and the base hist() function needs it as numeric
hist(as.numeric(Perthtemp))
```
### improve aesthetic
```{r}
# outliner ID 3

library(tidyverse)
#define where the breaks in histogram
userbreak <- c(8,10,12,14,16,18,20,22,24,26)

#remove the ID and the site columns
Perthtemp <- Aucitytemp2 %>% 
  filter(site=="Perth")

t <- Perthtemp %>% 
  dplyr::select(Jan:Dec)

hist((as.numeric(t)),
     breaks=userbreak,
     col="red",
     main="Histogram of Perth Temperature",
     xlab="Temperature",
     ylab="Frequency")
```
### check out the histogram
```{r}
histinfo <- as.numeric(t) %>% hist
histinfo
```
## 2.3 using more data
```{r}
plot(Ausoutline$geom)
```
### st_simplify
```{r}
AusoutSIMPLE <- Ausoutline %>% 
  st_simplify(.,preserveTopology=TRUE,dTolerance = 1000) %>% 
  # the argument dTolerance controls the level of generalisation in the units of the map
  # preserveTopology to TRUE or FALSE, when true it means that polyongs aren’t removed and holes in polygons are retained
  st_geometry() %>% 
  plot()
```
### projection conflict
```{r}
# make sure both layers in same CRS
print(Ausoutline)

crs(worldclimtemp)
```
### crop data
```{r}
Austemp <- Ausoutline %>% 
  #crop temp data to the extent
  terra::crop(worldclimtemp,.) # terra::crop(worldclimtemp,Ausoutline)

#plot the output
plot(Austemp)
```
### extract by mask
```{r}
exactAus <- terra::mask(Austemp,Ausoutline)
# mask(tif,shp)
```
### plot march
```{r}
# subset using the known location of the raster
hist(exactAus[[3]],col="red",main="March Temperature")
```
## 2.4 histogram with ggplot
### convert to tibble
```{r}
# make our raster into a data.frame to be compatible with ggplot2, using a dataframe or tibble
exactAusdf <- exactAus %>% 
  as.data.frame()
```
### ggplot
```{r}
library(ggplot2)
```
### 2.4.1 plot1 single month with mean
```{r}
gghist <- ggplot(exactAusdf,
                 aes(x=Mar))+
  geom_histogram(color="black",
                 fill="white")+
  labs(title="Ggplot2 histogram of Australian March temperatures",
       x="Temperature",
       y="Frequency")

# add a vertical line to the hisogram showing mean temperature
gghist + 
  geom_vline(aes(xintercept=mean(Mar,
                                      na.rm=TRUE)),
             # any missing values should be ignored when calculating the mean
                  color="blue",
                  linetype="dashed",
                  size=1)+  # line thickness
  theme(plot.title = element_text(hjust=0.5))
  # centers the title by setting the horizontal justification (hjust) to 0.5
```
### 2.4.2 plot2 multiple months
#### pivot_longer
```{r}
# plot multiple months of temperature data on the same histogram

## put our variable (months) into a one column using pivot_longer()
## select columns 1-12 (all the months) and place them in a new column called Month and their values in another called Temp

squishdata <- exactAusdf %>% 
  pivot_longer(
    cols = 1:12,
    names_to = "Month",
    values_to = "Temp"
  )
```
#### suset and select 2 months
```{r}
twomonths <- squishdata %>% 
  filter(.,Month=="Jan" | Month=="Jun")
```
#### mean of each month
```{r}
meantwomonths <- twomonths %>% 
  group_by(Month) %>% 
  summarise(Mean=mean(Temp,
                      na.rm=TRUE))
# any missing values should be ignored when calculating the mean
```
#### plot 
```{r}
ggplot(twomonths,
       aes(x=Temp,color=Month,fill=Month))+
  # color=Month and fill=Month: The "Month" variable is used to differentiate the two months by color and fill.
  geom_histogram(position="identity", 
                 # ensures that the bars are positioned directly over the x-values without any stacking.
                 alpha=0.5)+
  geom_vline(data=meantwomonths,
             aes(xintercept= Mean,
                 color=Month),
             linetype="dashed")+
  labs(title="Ggplot2 histogram of Australian Jan and Jun temperatures",
       x="Temperature",
       y="Frequency")+
  theme_classic()+
  # classic theme provides a simple and clean appearance to the plot
  theme(plot.title = 
          # "plot.title" refers to the title that you set using the labs(title = ...) function 
          element_text(hjust = 0.5))# element_text function to specify text properties
  # theme function customize various aspects of the plot's appearance, such as text size, colors, axis labels, and more
  
```

```{r}
data_complete_cases <- squishdata %>%
  drop_na()%>% 
  mutate(Month = factor(Month, levels = c("Jan","Feb","Mar",
                                          "Apr","May","Jun",
                                          "Jul","Aug","Sep",
                                          "Oct","Nov","Dec")))

# Plot faceted histogram
ggplot(data_complete_cases, aes(x=Temp, na.rm=TRUE))+
  geom_histogram(color="black", binwidth = 5)+
  labs(title="Ggplot2 faceted histogram of Australian temperatures", 
       x="Temperature",
       y="Frequency")+
  facet_grid(Month ~ .)+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
library(plotly)
# split the data for plotly based on month

jan <- squishdata %>%
  drop_na() %>%
  filter(., Month=="Jan")

jun <- squishdata %>%
  drop_na() %>%
  filter(., Month=="Jun")

# give axis titles
x <- list (title = "Temperature")
y <- list (title = "Frequency")

# set the bin width
xbinsno<-list(start=0, end=40, size = 2.5)

# plot the histogram calling all the variables we just set
ihist<-plot_ly(alpha = 0.6) %>%
        add_histogram(x = jan$Temp,
        xbins=xbinsno, name="January") %>%
        add_histogram(x = jun$Temp,
        xbins=xbinsno, name="June") %>% 
        layout(barmode = "overlay", xaxis=x, yaxis=y)

ihist
```




