# Gender Inequality Index TASK - Week 4

  Read in global gender inequality data
  Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019
  Share it with the World on GitHub
  
  Tip the countrycode R package will be helpful
  https://github.com/vincentarelbundock/countrycode

  Tip the gender inequality has changed in the last year, you will find what you need in the “All composite indices and components time series (1990-2021)” dataset, the metadata file beneath it will explain what the columns are.
  
## packages
```{r}
library(sf)
library(janitor)
library(tidyverse)
library(terra)
library(ggplot2)
library(remotes)
```

## countrycode package
```{r}
# install.packages("countrycode")

# install_github('vincentarelbundock/countrycode')
```

## read data

* HDI data from: https://hdr.undp.org/data-center/documentation-and-downloads
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41 
```{r}
HDR <- read_csv("wk4/data/HDR21-22_Statistical_Annex_GII_Table.csv",
                locale = locale(encoding = "latin1"),
                na = " ", skip=0)

World <- st_read("wk4/data/World_Countries_Generalized/World_Countries_Generalized.shp")
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column 

Some notes:

* COW codes = correlates of war codes
* ISO = International Organization for Standardization with 2 or 3 letters...

```{r}
HDIcols<- HDI %>%
  clean_names()%>%
  select(iso3, country, gii_2019, gii_2010)%>%
  mutate(difference=gii_2019-gii_2010)%>%
  #not needed here as we can now use the country name...but see below
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))%>%
  mutate(iso_code2=countrycode(iso3, origin ='iso3c', destination = 'iso2c'))

  
```

