# Gender Inequality Index TASK - Week 4

1. Read in global gender inequality data
2. Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019
  Share it with the World on GitHub
  
  Tip the countrycode R package will be helpful
  https://github.com/vincentarelbundock/countrycode

  Tip the gender inequality has changed in the last year, you will find what you need in the “All composite indices and components time series (1990-2021)” dataset, the metadata file beneath it will explain what the columns are.
  
## packages
```{r}
library(sf)
library(janitor)
library(tidyverse)
library(terra)
library(ggplot2)
library(remotes)
library(countrycode)
library(readr)
library(countrycode)
library(ggspatial)
library(RColorBrewer)
library(viridis)
library(showtext) # to change font
```

## countrycode package
```{r}
# install.packages("countrycode")

# install_github('vincentarelbundock/countrycode')
```

## read data

* HDI data from: https://hdr.undp.org/data-center/documentation-and-downloads
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41 

```{r}
HDI <- read_csv("wk4/data/HDR21-22_Composite_indices_complete_time_series.csv",
                locale = locale(encoding = "latin1"),
                na = " ", skip=0)

World <- st_read("wk4/data/World_Countries_Generalized/World_Countries_Generalized.shp")
```


## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column 

Some notes:

* `COW codes` = correlates of war codes
* `ISO` = International Organization for Standardizati
on with 2 or 3 letters...

```{r}
HDIcols<- HDI %>%
  clean_names()%>%
  select(iso3, country, gii_2019, gii_2010)%>%
  mutate(difference=gii_2019-gii_2010)%>%
  #not needed here as we can now use the country name...but see below
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))%>%
  mutate(iso_code2=countrycode(iso3, origin ='iso3c', destination = 'iso2c'))

  
```

## Join

Join the csv to world shape file

```{r}
Join_HDI <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("iso" = "iso_code"))

# 261 if using "aff_iso", 251 if using "iso". Could filter out the NA values.
```

```{r}
Join_HDI_2 <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("country" = "country"))
#251

```

# Problems 

* With Join_HDI there are 11 rows for Antarctica if using aff_iso - be sure to use iso column or remove the NA values as in the aff_iso Antarctica is NA

* With Join_HDI_2 the entries for other islands aren't joined as they don't have the same name...e.g. France, French Guiana, French Southern Territories.....

```{r}
Join_HDI_FR<-Join_HDI %>%
  filter(aff_iso=="FR")

Join_HDI_2_FR<-Join_HDI_2 %>%
  filter(aff_iso=="FR")
```














# Load Data


```{r}
# source: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-0.002619%2C0.000000%2C1.00
world_map<- st_read("wk4/data/World_Countries_Generalized/World_Countries_Generalized.shp")

# source: https://hdr.undp.org/sites/default/files/2021-22_HDR/HDR21-22_Composite_indices_complete_time_series.csv
gii_table <- read_csv("wk4/data/HDR21-22_Composite_indices_complete_time_series.csv") %>%
  dplyr::select(., iso3, country, contains("gii"))

```

# Analyze data

```{r}

# Create ISO-2 character for merging with map data, and
# calculate the difference between 2019 and 2010
gii_table2 <- gii_table %>%
  dplyr::mutate(
    .,
    iso2c = countrycode(iso3, origin = "iso3c", destination = "iso2c"),
    .before = country
  ) %>%
  dplyr::mutate(
    .,
    gii_diff = gii_2019 - gii_2010,
    .after = country
  )

# Join map data with statistics
gii_map <- world_map %>%
  left_join(
    .,
    gii_table2,
    by = c("ISO" = "iso2c")
  )


```

# create map

```{r}
# add fonts
font_add_google("Fira Sans")
showtext_auto()

# ggplot 
plot <- 
  ggplot(data = gii_map) +
  geom_sf(
    aes(fill = gii_diff, alpha = "No Data"), # add alpha to show 2nd legend for NA
    color = "white",
    lwd = 0.3
  ) + 

  # set title and caption
  labs(
    title = "Change in Gender Inequality between 2010 and 2019",
    caption = "Source: UNDP Human Development Reports (https://hdr.undp.org/data-center/documentation-and-downloads)"
  ) +

  # change scale aesthetics
  scale_fill_viridis(
    option = "magma",
    begin = 0,
    end = 1,
    name = "Difference in GII",
    na.value = "white",
    guide = guide_colorbar(
      direction = "horizontal",
      reverse = TRUE,
      barwidth = 20,
      barheight = 0.5,
      title.position = "top",
      title.hjust = 0.6,
      label.position = "bottom",
    )
  ) + 
  
  # scale for no data
  scale_alpha_manual(
    name = " ",
    values = 1,
    guide = guide_legend(
      keywidth = 3,
      keyheight = 0.5,
      title.position = "top",
      label.position = "bottom",
      override.aes = list(fill = "white")
    )
  ) +
  
  # aesthetics
  theme(
    plot.background = element_rect(fill = "lightcyan4", linewidth = 0),
    panel.background = element_rect(fill = "lightcyan4"),
    text = element_text(
      color = "white",
      family = "Fira Sans"
    ),
    plot.title = element_text(
      size = 20,
      margin = margin(t = 10, b = 10),
      hjust = 0.5
    ),
    legend.title = element_text(size = 15),
    legend.position = "bottom",
    legend.background = element_blank()
  ) 

plot
```

# Save Plot as image

Before saving the plot, the size of text has been modified.

```{r}
# change the theme to save
save <- plot + 
  theme(
    text = element_text(
      size = 30,
    ),
    plot.title = element_text(
      size = 50,
    ),
    legend.title = element_text(size = 30),
  ) 
  
# save ggplot to image
ggsave(
  "wk4/GII.png",
  plot = save,
  height = 7,
  width = 7)


```
