# Ineqaulity task - week 4

### Read in data:

Located within the Data folder:

* HDI data from: https://hdr.undp.org/data-center/documentation-and-downloads
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41 

## Load packages
```{r}
library(tidyverse)
library(sf)
library(here)
library(janitor)
#library(countrycode)
```

```{r}
HDI <- read_csv(here::here("homework_4", "HDR21-22_Composite_indices_complete_time_series.csv"),
                       locale = locale(encoding = "latin1"),
                       na = " ", skip=0)
World <- st_read("homework_4/World_Countries_(Generalized)/World_Countries__Generalized_.shp")
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column 

Some notes:

* COW codes = correlates of war codes
* ISO = International Organization for Standardization with 2 or 3 letters...

```{r}
HDIcols<- HDI %>%
  clean_names()%>%
  select(iso3, country, gii_2019, gii_2010)%>%
  mutate(difference=gii_2019-gii_2010)%>%
  #not needed here as we can now use the country name...but see below
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))%>%
  mutate(iso_code2=countrycode(iso3, origin ='iso3c', destination = 'iso2c'))

  
```

## Join

Join the csv to world shape file

```{r}
Join_HDI <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("iso" = "iso_code"))

# 261 if using "aff_iso", 251 if using "iso". Could filter out the NA values.
```

```{r}
Join_HDI_2 <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("country" = "country"))
#251

```

# Problems 

* With Join_HDI there are 11 rows for Antarctica if using aff_iso - be sure to use iso column or remove the NA values as in the aff_iso Antarctica is NA
* With Join_HDI_2 the entries for other islands aren't joined as they don't have the same name...e.g. France, French Guiana, French Southern Territories.....

```{r}
Join_HDI_FR<-Join_HDI %>%
  filter(aff_iso=="FR")

Join_HDI_2_FR<-Join_HDI_2 %>%
  filter(aff_iso=="FR")
```


...next time we will make a map using different repos
